---
title: "Assignment 2 (SCEM)"
author: "Keli Niu"
date: "2024-09-25"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Data Wrangling


## 1.1 (Q1)   

<!-- Include your answers for each question under a second level heading eg ## 1.1 (Q1) -->
```{r Q1, echo=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)  
library(Stat2Data)
data("Hawks")

hSF <- try({
  Hawks %>%
     
    filter(Species == "RT", Weight >= 1000) %>% 
    select(Wing, Weight, Tail)
}, silent = FALSE)

if (inherits(hSF, "try-error")) {
  print("An error occurred in filtering or selecting data.")
} else {
  print(head(hSF,5))
}

```
## 1.1 (Q2)   
```{r Q2, echo=FALSE}
num_variables <- ncol(hSF)  
num_examples <- nrow(hSF)   


print(paste("Number of variables in the data frame hSF is:", num_variables))
print(paste("Number of examples in the data frame hSF is:", num_examples))
```
## 1.2 (Q1)
```{r 1.2Q1, echo=FALSE}
sorted_hSF <- hSF %>%
  arrange(Wing)

sorted_hSF <- head(sorted_hSF, 5)
print(sorted_hSF)
```

## 1.3 (Q1)
```{r 1.3Q1, echo=FALSE}
hawkSpeciesNameCodes <- data.frame(
  species_code = c("CH", "RT", "SS"),
  species_name_full = c("Cooper's", "Red-tailed", "Sharp-shinned"),
  stringsAsFactors = FALSE
)
print(hawkSpeciesNameCodes)
```

## 1.3 (Q2)
```{r 1.3Q2, echo=FALSE}
library(dplyr)
hawksFullName<-Hawks %>%
  rename(OldSpecies = Species)%>%
  left_join(hawkSpeciesNameCodes, by = c("OldSpecies" = "species_code")) %>%
  rename(Species = species_name_full) %>%
  select(-OldSpecies)
```

## 1.3 (Q3)
```{r 1.3Q3, echo=FALSE}

hawksFullName %>%
    select(Species, Wing, Weight) %>%
    head(7)


```
## 1.4 (Q1)
```{r 1.4Q1, echo=FALSE}
hawksWithBMI <- Hawks %>%
  mutate(bird_BMI = 1000*(Weight / (Wing^2))) %>%
  select(Species, bird_BMI) %>%
  arrange(desc(bird_BMI))

print(head(hawksWithBMI, 8))


```
## 1.5 (Q1)
```{r 1.5Q1, echo=FALSE}

summary_table<-hawksFullName%>%
  group_by(Species)%>%
  summarize(
    num_rows = n(),  
    mn_wing = mean(Wing / 10, na.rm = TRUE), 
    nd_wing = median(Wing / 10, na.rm = TRUE),  
    t_mn_wing = mean(Wing / 10, trim = 0.1, na.rm = TRUE),  
    b_wt_ratio = max(Wing / Tail, na.rm = TRUE)  
  )
print(summary_table)

```
## 1.5 (Q2)
```{r 1.5Q2, echo=FALSE}

summary_table_missing <- hawksFullName %>%
  select(Species, Wing, Weight, Culmen, Hallux, Tail, StandardTail, Tarsus, Crop) %>%
  group_by(Species) %>%
  summarize(across(everything(), ~ sum(is.na(.))), .groups = 'drop')


print(summary_table_missing)

```

# 2. Random experiments, events and sample spaces, and the set theory
## 2.1 (Q1)
**Random Experiment :** A random experiment is a procedure that has a defined set of possible outcomes and can be repeated multiple times in principle.

**Event :**  An event is a collection of possible outcomes from a random experiment. It is distinct from an outcome itself, although it can consist of a single outcome. An event is considered to have occurred if it includes the actual outcome of the experiment.

**Sample Space :** The sample space is the complete set of all possible outcomes of interest for a random experiment. It represents the largest possible event within the context of the experiment.

## 2.1 (Q2)
**Example :** An example of an event in this random experiment could be rolling a sum of 10. This event includes all outcome combinations where the numbers on the two dice add up to 10, such as (4, 6), (5, 5), and (6, 4).

**Sample Space :** $$
S = \{(i, j) \mid i, j \in \{1, 2, 3, 4, 5, 6\}\}
$$

**The total number of different events :** \( 2^{36} \)：

**Is the empty set considered as an event?** Yes. It represents the impossible event that contains no outcomes.


# 3. Probability theory

## 3.1 (Q1)
```{r 3.1Q1, echo=TRUE}
P <- function(event) {
  event <- sort(event)  
  if (identical(event, c("a", "b"))) {
    return(0.6)
  } else if (identical(event, c("b", "c"))) {
    return(0.5)
  } else if (identical(event, c("a"))) {
    return(0.5)
  } else if (identical(event, c("b"))) {
    return(0.1)
  } else if (identical(event, c("c"))) {
    return(0.4)
  } else if (identical(event, c("a", "c"))) {
    return(0.9)  
  } else if (identical(event, c("a", "b", "c"))) {
    return(1.0)
  } else if (length(event) == 0) {  
    return(0.0)
  } else {
    return("Undefined") 
  }
}

print(P(c("a", "b")))


```
## 3.1 (Q2)
```{r 3.1Q2, echo=TRUE}

```
.....



