---
title: "Assignment 3"
author: "Keli Niu"
date: "2024-10-01"
output: html_document # you can change to other output format if you want
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Visualisation


## 1 (Q1)   
```{r Q1, echo=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)  
library(Stat2Data)
data("Hawks")

hawksSmall <- drop_na(select(Hawks, Age, Day, Month, Year, CaptureTime, Species, Wing, Weight, Tail))

dim(hawksSmall)


head(hawksSmall, 5)

```


## 1 (Q2)   
```{r Q2}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
ggplot(hawksSmall, aes(x = Weight)) +
  geom_histogram(binwidth = 10) +
  labs(title = "Histogram of Hawks' Weights", x = "Weight", y = "Count") 
```

## 1 (Q3)

```{r Q3, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
plot1 <- ggplot(hawksSmall, aes(x = Tail)) +
  geom_density(adjust = 0.5) +
  labs(title = "Density Plot of Hawks' Tail Lengths (adjust = 0.5)",
       x = "Tail Length (mm)", y = "Density") 

plot2 <- ggplot(hawksSmall, aes(x = Tail)) +
  geom_density(adjust = 2) +
  labs(title = "Density Plot of Hawks' Tail Lengths (adjust = 2)",
       x = "Tail Length (mm)", y = "Density") 

plot1
plot2

```

The main difference between the two plots is the level of smoothness. The second plot is smoother, and compared to the first plot, it loses some of the finer details. The first plot shows three distinct groupings, so it has three modes. The second plot, on the other hand, has two groupings, resulting in two modes.



  
  
## 1 (Q4)

```{r Q4, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
ggplot(hawksSmall, aes(x = Tail, color = Species)) +
  geom_density(adjust = 2) +
  labs(title = "Density Plot of Tail Lengths by Species",
       x = "Tail length ", y = "Count") 

```

## 1 (Q5)

```{r Q5, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
ggplot(hawksSmall, aes(x = Tail, y = Species, fill = Species)) +
  geom_violin() + theme_bw()+
  labs(title = "Violin Plot of Tail Lengths by Species",
       x = "Tail (mm)", y = "Density")

```

## 1 (Q6)

```{r Q6, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
ggplot(hawksSmall, aes(x = Tail, y = Weight, colour = Species)) +
  geom_point() + theme_bw()+
  labs(x = "Tail (mm)", y = "Weight (mm)")

```

1. There are three aesthetics: Tail(x-axis), Weight(y-axis), Species(color)
2. The glyphs within this plot are points, which repersent the relationship between the Tail and the Weight.
3. position, colour

## 1 (Q7)

```{r Q7, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
ggplot(hawksSmall, aes(x = Tail, y = Weight, colour = Species)) +
  geom_point() + 
  geom_smooth(method=lm)+
  facet_wrap(~Species, scales = "free")+
  theme_bw()+
  labs(x = "Tail (mm)", y = "Weight (mm)")

```

1. Shape, colour, position
2. There is a positive correlation between the weight and tail length of hawks in all three species, meaning that the longer the tail, the heavier the hawk. Among them, the CH species has a more dispersed distribution, with a weaker correlation, indicating that other factors may be influencing the weight. Additionally, both RT and SS species show a stronger correlation, with RT having a steeper slope, indicating that tail length has a greater impact on weight.

## 1 (Q8)

```{r Q8, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hawkHeaviest<-hawksSmall%>%
  filter(Weight==max(Weight))%>%
  select(Weight, Tail, Species)

hawkHeaviest

ggplot(hawksSmall, aes(x = Tail, y = Weight, colour = Species)) +
  geom_point() + theme_bw()+
  labs(x = "Tail (mm)", y = "Weight (mm)")+
  
annotate("text",x = hawkHeaviest$Tail, y = hawkHeaviest$Weight-200, label = "heaviest hawk")+
annotate("curve", x = hawkHeaviest$Tail, y = hawkHeaviest$Weight-200 ,xend = hawkHeaviest$Tail, yend = hawkHeaviest$Weight,curvature = 0.5, arrow = arrow(length = unit(0.2, "cm")))

```

# 2. Finite probability spaces

## 2.1 (Q1)   
$$
P(Z = z) = \binom{22}{z} \cdot \left(\frac{3}{10}\right)^z \cdot \left(\frac{7}{10}\right)^{22-z}
$$

## 2.1 (Q2)   


```{r 2.1Q2, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
prob_red_spheres<-function(z){
  n<-22
  p<-3/10
  
  probability<-choose(n,z)*(p^z)*((1-p)^(n-z))
  return(probability)
  
}

prob_red_spheres(10)

```

## 2.1 (Q3)   


```{r 2.1Q3, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

num_reds <- 1:22
prob <- numeric(length(num_reds))
for (i in num_reds) {
  prob[i] <- prob_red_spheres(i)  
}

prob_by_num_reds<-data.frame(num_reds,prob)

head(prob_by_num_reds,3)


```


## 2.1 (Q4)   


```{r 2.1Q4,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

ggplot(prob_by_num_reds, aes(x = num_reds, y = prob)) +
  geom_line() +  
  labs(title = "Probability of Drawing Red Spheres", 
       x = "Number of Reds", 
       y = "Probability") + theme_bw()

```

## 2.1 (Q5)   


```{r 2.1Q5, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sample(10, 22, replace=TRUE)

## case 1: Setting the random seed just once
set.seed(0)
for(i in 1:5){
 print(sample(100,5,replace=FALSE))
 # The result may well differ every time
}
## case 2: Resetting the random seed every time
set.seed(1)
print(sample(100,5,replace=FALSE))
set.seed(1)
print(sample(100,5,replace=FALSE))
set.seed(1)
print(sample(100,5,replace=FALSE))
# The result should not change
## case 3: reproducing case 1 if we set a random seed at the beginning.
set.seed(0)
for(i in 1:5){
 print(sample(100,5,replace=FALSE))
} # The result will be 5 samples exactly the same as in case 1 (why?).


itermap <- function(.x, .f) {
 result <- list()
 for (item in .x) {
 result <- c(result, list(.f(item)))
 }
 return(result)
}
itermap( c(1,2,3), function(x){ return(c(x,x^2)) } )


itermap_dbl <- function(.x, .f) {
 result <- numeric(length(.x))
 for (i in 1:length(.x)) {
 result[i] <- .f(.x[[i]])
 }
 return(result)
}
itermap_dbl( c(1,2,3), function(x){ return(x^3) } )

num_trials<-1000 # set the number of trials
set.seed(0) # set the random seed
sampling_with_replacement_simulation<-data.frame(trial=1:num_trials)%>%
  mutate(sample_balls = itermap(.x=trial, function(x){sample(10,22,replace = TRUE)}))
# generate collection of num_trials simulations

sampling_with_replacement_simulation <- sampling_with_replacement_simulation%>%
  mutate(num_reds = sapply(sample_balls, function(x) sum(x <= 3)))


head(sampling_with_replacement_simulation)
```

## 2.1 (Q6)   


```{r 2.1Q6, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

 num_reds_in_simulation<-sampling_with_replacement_simulation %>%
 pull(num_reds)
# we extract a vector corresponding to the number of reds in each trial
prob_by_num_reds<-prob_by_num_reds %>%
 mutate(predicted_prob=itermap_dbl(.x=num_reds, function(.x)
sum(num_reds_in_simulation==.x))/num_trials)
# add a column which gives the number of trials with a given number of reds
head(prob_by_num_reds)


```

## 2.1 (Q7)   


```{r 2.1Q7, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

prob_by_num_reds %>%
 rename(TheoreticalProbability=prob,
EstimatedProbability=predicted_prob) %>%
 ggplot() + geom_line(aes(x=num_reds, y=TheoreticalProbability)) +
 geom_line(aes(x=num_reds, y=EstimatedProbability), linetype='dashed')+
 geom_point(aes(x=num_reds, y=EstimatedProbability)) +
 theme_bw() + xlab("Number of reds") + ylab("Probabilities")


```

## 2.2 (Q1)   


```{r 2.2Q1, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)


set.seed(0)


num_trials <- 1000
  
sample_size <- 10    
num_balls <- 100     

balls <- c(rep("red", 20), rep("blue", 20), rep("green", 60))

itermap_dbl <- function(.x, .f) {
  result <- numeric(length(.x))
  for (i in 1:length(.x)) {
    result[i] <- .f(.x[[i]])
  }
  return(result)
}

sampling_without_replacement_simulation <- data.frame(trial = 1:num_trials) %>%
  mutate(sample_balls = itermap(trial, function(x) sample(balls, sample_size, replace = FALSE))) %>%
  mutate(num_reds = itermap_dbl(sample_balls, function(x) sum(x == "red")),
         num_blues = itermap_dbl(sample_balls, function(x) sum(x == "blue")),
         num_greens = itermap_dbl(sample_balls, function(x) sum(x == "green"))) %>%
  mutate(missing_color = pmin(num_reds, num_blues, num_greens) == 0)

prob_missing_color <- mean(sampling_without_replacement_simulation$missing_color)

prob_missing_color


```





